---
title: "linear-regression-tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linear-regression-tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linearReg)
```

# Function Explanations
*For BIOSTAT625 homework 3, to fit a linear regression model, we use `fitLinearModel()` function which need two parameters input:
1. a formula for linear regression: $Y \sim X$
2. a dataset containing $X$ and $Y$ variables used in the above formula

*To get model summary including estimtaed coefficients, standard errors, test statistics, p-values, R squared, etc, we use `model_summary()` function and pass `model` as the parameter, which is the output of `fitLinearModel()`. 

*You can get various model results separately by passing `model` parameter to below functions:
1. confidence intervals of all estimated coefficients: `getConfidenceInterval()`
2. R squared: `getRSquared()`
3. adjusted R squared: `getAdjustedRSquared()`
4. F Statistic: `getFStatistic()`


# Examples
```{r}
# Define the formula
formula = Petal.Length ~ Petal.Width + Sepal.Width
```

1. Fit linear regression model using `fitLinearModel()`
```{r}
my_mod <- fitLinearModel(formula, iris)
```

2. Display model summary
```{r}
model_summary(my_mod)
```

3. Display model Confidence Intervals
```{r}
getConfidenceInterval(my_mod)
```



