---
title: "linear-regression-tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{linear-regression-tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Loading Packages
```{r setup}
# install `linearReg` package if you haven't installed yet
# install.packages("linearReg")
library(linearReg)
```

# Function Explanations
*For BIOSTAT625 homework 3, to fit a linear regression model, we use `fitLinearModel()` function which need two parameters input:
1. a formula for linear regression: $Y \sim X$
2. a dataset containing $X$ and $Y$ variables used in the above formula

*To get model summary including estimtaed coefficients, standard errors, test statistics, p-values, R squared, etc, we use `model_summary()` function and pass `model` as the parameter, which is the output of `fitLinearModel()`. 

*You can get various model results separately by passing `model` parameter to below functions:
1. confidence intervals of all estimated coefficients: `getConfidenceInterval()`
2. R squared: `getRSquared()`
3. adjusted R squared: `getAdjustedRSquared()`
4. F Statistic: `getFStatistic()`


# Examples
```{r}
# Define the formula
formula = Petal.Length ~ Petal.Width + Sepal.Width
```

1. Fit linear regression model using `fitLinearModel()`
```{r}
my_mod <- fitLinearModel(formula, iris)
```

(a) Calculate estimated coefficients:
```{r}
my_mod$coefficients
```
(b) Calculate estimated coefficient standard errors:
```{r}
my_mod$SE_beta_hat
```

(c) Calculate mean squared error (sigma squared)
```{r}
my_mod$MSE
```

(d) Calculated R squared
```{r}
my_mod$R_squared
```

(e) Calculated adjusted R squared
```{r}
my_mod$adjusted_R_squared
```

(f) Calculated F statistics
```{r}
my_mod$F_statistic
```


2. Display model summary
```{r}
model_summary(my_mod)
```

3. Display model confidence intervals for each coefficient
```{r}
getConfidenceInterval(my_mod)
```

4. Display R squared for fitted model
```{r}
getRSquared(my_mod)
```

5. Display adjusted R squared for fitted model
```{r}
getAdjustedRSquared(my_mod)
```

6. Display F statistic and p-value for fitted model
```{r}
getFStatistic(my_mod)
```
# Compare with Standard lm() model
```{r}
# Fit models using both lm() and your custom function
lm_model <- lm(Petal.Length ~ Petal.Width + Sepal.Length, data = iris)
custom_model <- fitLinearModel(Petal.Length ~ Petal.Width + Sepal.Length, data = iris)

# Compare coefficients
all.equal(coef(lm_model), custom_model$coefficients)

# Compare standard errors
all.equal(summary(lm_model)$coefficients[, "Std. Error"], custom_model$SE_beta_hat)

# Compare R-squared values
all.equal(summary(lm_model)$r.squared, custom_model$R_squared)

# Compare adjusted R-squared values
all.equal(summary(lm_model)$adj.r.squared, custom_model$adjusted_R_squared)

```


```{r}
# Load necessary package
library(bench)

# using bench::mark to compare the efficiency of customized and standard linear regression model fittings. 
benchmark_model_fitting<- bench::mark(
  my_mod_coef = fitLinearModel(Petal.Length ~ Petal.Width + Sepal.Width, iris)$coefficients,
  lm_model_coef = coef(lm(Petal.Length ~ Petal.Width + Sepal.Width, data = iris)),
  iterations = 100
)

print(benchmark_model_fitting)
```

```{r}
# benchmark_ci <- bench::mark(
#   my_mod_ci = as.numeric(unlist(getConfidenceInterval(my_mod))),
#   lm_model_ci = as.vector(confint(lm_model)),
#   iterations = 100
# )
# 
# print(benchmark_ci)
benchmark_ci <- bench::mark(
  my_mod_ci = { getConfidenceInterval(my_mod); NULL }, 
  lm_model_ci = { confint(lm_model); NULL },            
)

# Print the benchmark results
print(benchmark_ci)
```

```{r}
benchmark_r_squared <- bench::mark(
  my_mod_r2 = { my_mod$R_squared; NULL },
  lm_model_r2 = { summary(lm_model)$r.squared; NULL },
  iterations = 100
)

print(benchmark_r_squared)
```

```{r}
benchmark_adjusted_r_squared <- bench::mark(
  my_mod_adj_r2 = { getAdjustedRSquared(my_mod); NULL },
  lm_model_adj_r2 = { summary(lm_model)$adj.r.squared; NULL },
  iterations = 100
)

print(benchmark_adjusted_r_squared)
```


```{r}
# Benchmark F-statistics calculation
benchmark_f_stat <- bench::mark(
  my_mod_f_stat = { getFStatistic(my_mod); NULL },
  lm_model_f_stat = { as.numeric(summary(lm_model)$fstatistic[1]); NULL },
  iterations = 100
)

print(benchmark_f_stat)
```


